---
title: "total_stats"
author: "Grace Chung"
date: "2023-04-12"
output: html_document
---

# Load Packages
```{r}
library('tidyverse')
library('lme4')
library('lmerTest')
library("tidymodels")
library("ggtext")
library("ggpubr")
library("stats")
```

# Set working directory
```{r}
setwd("/Users/gracechungm/Desktop/Portfolio Materials/thesis/Code/Metadata for R/")
```

# Set figure parameters: sizes for text, points, and axes
```{r}
text_size = 15
triangle_size = 1.5 
cross_size = 1.5
axis_size = 20
```

# Create dataframes by importing csv's.
## Make dataframes for the 12-30C treatments by importing the spring_natural csv. 
```{r}
# dataframe of all data for the 12-30C treatments.
spring_df <- read.csv("spring_natural.csv")%>% select(-("bubble_dist_mm"))

# dataframe for all 12-30C trials that have a measured bubble size.
spring_size <- spring_df[!is.na(spring_df$max_size_mm2),]

# dataframe for all 12-30C trials that have a measured sound pressure level (SPL).
spring_SPL <- spring_df[!is.na(spring_df$max_SPL),] 
```

## Make a dataframe (all_33) of all data for the 33C treatment by importing both the spring_33 and summer_33 csv.
```{r}
spring_33 <- read.csv("spring_33.csv") %>% select(c(shrimp_ID, video_ID, Temperature, acc_hr, use_SPL, max_SPL, body_mass_g, DactylLength_mm, use_distance, use_bubble, max_size_mm2, growth_ms, collapse_ms, rebound_ms, col_rate_mm2pms))

summer_33 <- read.csv("summer_33.csv") %>%  select(c(shrimp_ID,	video_ID,	acc_hr,	Temperature	,use_SPL,	max_SPL,	body_mass_g,	DactylLength_mm	,use_distance	,use_bubble,	max_size_mm2	,growth_ms,	collapse_ms,	rebound_ms,	col_rate_mm2pms))

# dataframe of all data for the 33C treatment.
all_33 <- rbind(spring_33,summer_33)
rm("spring_33","summer_33")

# dataframe for all 33C trials that have a measured bubble size.
size_33 <- all_33[!(all_33$use_bubble=="0"),]

# dataframe for all 33C trials that have a measured sound pressure level (SPL).
SPL_33 <- all_33[!(all_33$use_SPL=="0"),]
```

## Create a dataframe that combines the 12-30C (natural) treatments and the 33C (climate) treatment.
```{r}
# dataframe of all data in all treatments (12-33C).
total_df = rbind(all_33,spring_df)

# dataframe for all treatment trials that have a measured bubble size.
total_size <- total_df[!(total_df$use_bubble=="0"),]

# dataframe for all treatment trials that have a measured sound pressure level (SPL).
total_SPL <- total_df[!(total_df$use_SPL=="0"),]
```


# Linear Mixed Models (LMM) of 33C treatment
## Modeling Bubble Size (Random Effect (RE): Shrimp ID; Fixed Effects (FE): Dactyl Length, Body Mass) (33C)
```{r}
# Null hypothesis: RE = ID
size_33_null <- lmer(max_size_mm2 ~ (1 | shrimp_ID), REML =F, data = size_33)
AIC(logLik(size_33_null))

#FE = Dactyl Length
size_33_dactyl <- lmer(max_size_mm2 ~ DactylLength_mm + (1 | shrimp_ID), REML =F, data = size_33)
summary(size_33_dactyl)
AIC(logLik(size_33_dactyl))

#FE = Body Mass
size_33_body <- lmer(max_size_mm2 ~ body_mass_g + (1 | shrimp_ID), REML =F, data = size_33)
summary(size_33_body)
AIC(logLik(size_33_body))
```

## Modelling SPL (Random Effect (RE): Shrimp ID; Fixed Effects (FE): Dactyl Length, Body Mass) (33C)
```{r}
# Null hypothesis: RE = ID
SPL_33_null <- lmer(max_SPL ~ (1 | shrimp_ID), REML =F, data = SPL_33)
AIC(logLik(SPL_33_null))

#FE = Dactyl Length
SPL_33_dactyl <- lmer(max_SPL ~ DactylLength_mm + (1 | shrimp_ID), REML =F, data = SPL_33)
summary(SPL_33_dactyl)
AIC(logLik(SPL_33_dactyl))

#FE = Body Mass
SPL33_mass <- lmer(max_SPL ~ body_mass_g + (1 | shrimp_ID), REML =F, data = SPL_33)
summary(SPL33_mass)
AIC(logLik(SPL33_mass))
```

# LMM of 12-30C treatments
## Modelling Bubble Size (Random Effect (RE): Shrimp ID; Fixed Effects (FE): Temperature, Dactyl Length) (12-30C)
```{r}
#Null hypothesis: RE = Shrimp ID
spring_size_null <- lmer(max_size_mm2 ~ (1 | shrimp_ID), REML =F, data = spring_size)
AIC(logLik(spring_size_null))

#FE = Temperature
spring_size_temp <- lmer(max_size_mm2 ~ Temperature + (1 | shrimp_ID), REML =F, data = spring_size)
#summary(spring_size_temp)
AIC(logLik(spring_size_temp))

#FE = Dactyl Length
spring_size_dactyl <- lmer(max_size_mm2 ~ DactylLength_mm + (1 | shrimp_ID), REML =F, data = spring_size)
#summary(spring_size_dactyl)
AIC(logLik(spring_size_dactyl))
```

## Modelling SPL (Random Effect (RE): Shrimp ID; Fixed Effects (FE): Temperature, Dactyl Length, Bubble Size) (12-30C)
```{r}
#Null hypothesis: RE = ID
spring_SPL_null <- lmer(max_SPL ~ (1 | shrimp_ID), REML =F, data = spring_SPL)
#summary(spring_SPL_null)
AIC(logLik(spring_SPL_null))

#FE = Temperature
spring_SPL_temp <- lmer(max_SPL ~ Temperature + (1 | shrimp_ID), REML =F, data = spring_SPL)
#summary(spring_SPL_temp)
AIC(logLik(spring_SPL_temp))

#FE = Dactyl Length
spring_SPL_dactyl <- lmer(max_SPL ~ DactylLength_mm + (1 | shrimp_ID), REML =F, data = spring_SPL)
#summary(spring_SPL_dactyl)
AIC(logLik(spring_SPL_dactyl))


# Modelling SPL using Bubble Size as a predictor
#NULL HYPOTHESIS: RE = Bubble Size + Shrimp ID
spring_SPL_bubbleNULL <- lmer(max_SPL ~ (max_size_mm2 || shrimp_ID), REML =F, data = spring_SPL)
#summary(spring_SPL_bubbleNULL)
AIC(logLik(spring_SPL_bubbleNULL))

#FE = Bubble Size
spring_SPL_bubble <- lmer(max_SPL ~ max_size_mm2 + (max_size_mm2 || shrimp_ID), REML =F, data = spring_SPL)
#summary(spring_SPL_bubble)
AIC(logLik(spring_SPL_bubble))
```


# LMM of all treatments (12-33C)
## Modelling Bubble Size (Random Effect (RE): Shrimp ID; Fixed Effects (FE): Temperature, Dactyl Length) (12-33C)
```{r}
#Null hyp: RE ID
size_null <- lmer(max_size_mm2 ~ (1 | shrimp_ID), REML =F, data = total_size)
AIC(logLik(size_null))

#FE T
size_t <- lmer(max_size_mm2 ~ Temperature + (1 | shrimp_ID), REML =F, data = total_size)
summary(size_t)
AIC(logLik(size_t))

#FE DL
size_dactyl <- lmer(max_size_mm2 ~ DactylLength_mm + (1 | shrimp_ID), REML =F, data = total_size)
summary(size_dactyl)
AIC(logLik(size_dactyl))
```

## Modelling SPL (Random Effect (RE): Shrimp ID; Fixed Effects (FE): Temperature, Dactyl Length, Bubble Size) (12-33C)
```{r}
#Null hyp: RE = ID
spl_null <- lmer(max_SPL ~ (1 | shrimp_ID), REML =F, data = total_SPL)
AIC(logLik(spl_null))

#FE = T
spl_t <- lmer(max_SPL ~ Temperature + (1 | shrimp_ID), REML =F, data = total_SPL)
#summary(spl_t)
AIC(logLik(spl_t))

#FE = DL
spl_dactyl <- lmer(max_SPL ~ DactylLength_mm + (1 | shrimp_ID), REML =F, data = total_SPL)
#summary(spl_dactyl)
AIC(logLik(spl_dactyl))


#NULL HYP: RE = Bubble size + ID
SPL_bubbleNULL <- lmer(max_SPL ~ (max_size_mm2 || shrimp_ID), REML =F, data = total_SPL)
#summary(SPL_bubbleNULL)
AIC(logLik(SPL_bubbleNULL))

# FE = Bubble size
SPL_bubble <- lmer(max_SPL ~ max_size_mm2 + (max_size_mm2 || shrimp_ID), REML =F, data = total_SPL)
summary(SPL_bubble)
AIC(logLik(SPL_bubble))
```


# SPRING+SUMMER FIGURES
## (FIG 4A) Size by Temperature (12-30C + 33C)
```{r}
fig_Size_T <- ggplot(data = spring_size, aes(x=Temperature, y=max_size_mm2)) +
  geom_point(aes(color="Natural (12-30°C)"), shape = 3, size = cross_size) +
  geom_point(data = size_33, aes(color="Climate (33°C)"), shape= 17, size = triangle_size) +
  scale_color_manual(name=NULL, limits=c("Natural (12-30°C)", "Climate (33°C)"), values = c("black", "red")) +
  guides(color = guide_legend(override.aes = list(pch = c(3, 17), fill = c("black", "red")))) +
  theme_classic(base_size = axis_size) +
  theme(legend.position = "bottom",
        legend.text = element_text(size = text_size)) +
  labs(x="Temperature (°C)",
       y=bquote("Max Bubble Size "(mm^2)))+
  scale_y_continuous(breaks = seq(0,100, by = 10)) +
  scale_x_continuous(breaks = c(12,15,20,25,30,33))
fig_Size_T
```

## (FIG 4B) Size by Dactyl Length (12-30C + 33C)
```{r}
# FN from: (LMM) 12-33C (BLUE)
fun.totalsizeDL = function(x) -17.4775 + 7.3542*x

# FN from (LMM) 12-30C (BLACK)
fun.spring_sizeDL = function(x) -17.781  + 7.481*x

# FN from (LMM) 33C (RED)
fun.summer_sizeDL = function(x) -19.898  + 7.641*x

fig_Size_DL <- ggplot(data = spring_SPL, aes(x=DactylLength_mm, y=max_size_mm2)) +
  geom_point(aes(color="Natural (12-30°C)"), shape = 3, size = cross_size) +
  geom_point(data = SPL_33, aes(color="Climate (33°C)"), shape= 17, size = triangle_size) +
  scale_color_manual(name=NULL, limits=c("Natural (12-30°C)", "Climate (33°C)"), values = c("black", "red")) +
  guides(color = guide_legend(override.aes = list(pch = c(3, 17), fill = c("black", "red")))) +
  theme_classic(base_size = axis_size) +
  theme(legend.position = "bottom",
        legend.text = element_text(size = text_size)) +
  # stat_function(fun = fun.totalsizeDL, color = "blue") +
  stat_function(fun = fun.spring_sizeDL, color = "black") +
  stat_function(fun = fun.summer_sizeDL, color = "red") +
  labs(x="Dactyl Length (mm)",
       y="")+
  scale_y_continuous(breaks = seq(0,100, by = 10)) +
  scale_x_continuous(breaks = seq(0, 8, by = 1))
fig_Size_DL
```

## Arrange (FIGURE 4: A + B)
```{r}
ggarrange(fig_Size_T, fig_Size_DL, labels = c("A", "B"),
          common.legend = TRUE, legend = "bottom",
          ncol = 2, nrow = 1)
```


## (FIG 5A) SPL by Temperature (12-30C + 33C)
```{r}
fig_SPL_T <- ggplot(data = spring_SPL, aes(x=Temperature, y=max_SPL)) +
  geom_point(aes(color="Natural (12-30°C)"), shape = 3, size = cross_size) +
  geom_point(data = SPL_33, aes(color="Climate (33°C)"), shape= 17, size = triangle_size) +
  scale_color_manual(name=NULL, limits=c("Natural (12-30°C)", "Climate (33°C)"), values = c("black", "red")) +
  guides(color = guide_legend(override.aes = list(pch = c(3, 17), fill = c("black", "red")))) +
  theme_classic(base_size = axis_size) +
  theme(legend.position = c(0.15, 0.9),
        legend.text = element_text(size = text_size)) +
  labs(x="Temperature (°C)",
       y=bquote("Max SPL (dB re 1 µPa)"))+
  scale_y_continuous(breaks = seq(150,300, by = 10)) +
  scale_x_continuous(breaks = c(12,15,20,25,30,33))
fig_SPL_T
```

## (FIG 5B) SPL by Dactyl Length (12-30C + 33C)
```{r}
fig_SPL_DL <- ggplot(data = spring_SPL, aes(x=DactylLength_mm, y=max_SPL)) +
  geom_point(aes(color="Natural (12-30°C)"), shape = 3, size = cross_size) +
  geom_point(data = SPL_33, aes(color="Climate (33°C)"), shape= 17, size = triangle_size) +
  scale_color_manual(name=NULL, limits=c("Natural (12-30°C)", "Climate (33°C)"), values = c("black", "red")) +
  guides(color = guide_legend(override.aes = list(pch = c(3, 17), fill = c("black", "red")))) +
  theme_classic(base_size = axis_size) +
  theme(legend.position = c(0.15, 0.9),
        legend.text = element_text(size = text_size)) +
  labs(x="Dactyl Length (mm)",
       y=bquote(""))+
  scale_y_continuous(breaks = seq(150,300, by = 10)) +
  scale_x_continuous(breaks = seq(0, 8, by = 1))
fig_SPL_DL
```

## Arrange SPL (FIGURE 5: A + B)
```{r}
ggarrange(fig_SPL_T, fig_SPL_DL, labels = c("A", "B"),
          common.legend = TRUE, legend = "bottom",
          ncol = 2, nrow = 1)
```


## (FIG 6) SPL by Bubble Size (12-30C + 33C)
```{r}
# FN from: (LMM) 33C (RED)
fun.totalSPLsize = function(x) 191.97017 + 0.61187*x

# FN from: (LMM) 12-30C (BLACK)
fun.spring_SPLsize = function(x) 191.2322  + 0.5613*x
  
fig_SPL_size <- ggplot(data = spring_SPL, aes(x=max_size_mm2, y=max_SPL)) +
  geom_point(aes(color="Natural (12-30°C)"), shape = 3, size = 2) +
  geom_point(data = SPL_33, aes(color="Climate (33°C)"), shape= 17, size = 2) +
  scale_color_manual(name=NULL, limits=c("Natural (12-30°C)", "Climate (33°C)"), values = c("black", "red")) +
  guides(color = guide_legend(override.aes = list(pch = c(3, 17), fill = c("black", "red")))) +
  theme_classic(base_size = axis_size) +
  theme(legend.position = "bottom",
        legend.text = element_text(size = text_size)) +
    stat_function(fun = fun.totalSPLsize, color = "red") +
    stat_function(fun = fun.spring_SPLsize, color = "black") +
  labs(x=bquote("Max Bubble Size "(mm^2)),
       y=bquote("Max SPL (dB re 1 µPa)"))+
  scale_y_continuous(breaks = seq(150,300, by = 10)) +
  scale_x_continuous(breaks = seq(0, 70, by = 10))
fig_SPL_size
```
